\documentclass[paper=a4,fontsize=11pt]{article}

% Enhanced packages for modern CV
\usepackage[hidelinks]{hyperref}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage[svgnames]{xcolor}
\usepackage{fontawesome}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{array}
\usepackage{tabularx}
\usepackage{url}

% Professional color scheme
\definecolor{primary}{RGB}{41, 128, 185}     % Professional blue
\definecolor{secondary}{RGB}{52, 73, 94}     % Dark gray
\definecolor{accent}{RGB}{231, 76, 60}       % Accent red
\definecolor{text}{RGB}{44, 62, 80}          % Text color

% Geometry with better margins
\usepackage[top=1.5cm, bottom=1.5cm, left=2cm, right=2cm]{geometry}

\frenchspacing
\pagestyle{empty}

% Modern section styling
\titleformat{\section}
  {\Large\bfseries\color{primary}}
  {}{0em}
  {}[\color{primary}\titlerule]

\titlespacing*{\section}{0pt}{15pt}{8pt}

%%% Enhanced Macros for Professional Layout
%%% ------------------------------------------------------------
\newlength{\spacebox}
\settowidth{\spacebox}{8888888888}
\newcommand{\sepspace}{\vspace*{0.8em}}

% Professional name styling
\newcommand{\MyName}[1]{
	\begin{center}
		{\Huge\bfseries\color{primary} #1}
		\vspace{2pt}
	\end{center}
}

% Professional title/slogan
\newcommand{\MySlogan}[1]{
	\begin{center}
		{\Large\color{secondary}\textit{#1}}
		\vspace{8pt}
	\end{center}
}

% Modern section command
\newcommand{\NewPart}[1]{\section{#1}}

% Enhanced contact entry
\newcommand{\PersonalEntry}[2]{
	\noindent\hangindent=2em\hangafter=0
	\parbox{\spacebox}{
		\textbf{\color{secondary}#1}}
	\hspace{1.5em} #2 \par
}

% Skills entry with better formatting
\newcommand{\SkillsEntry}[2]{
	\noindent\hangindent=2em\hangafter=0
	\parbox{\spacebox}{
		\textbf{\color{primary}#1}}
	\hspace{1.5em} #2 \par
}
		
% Professional experience entry
\newcommand{\EducationEntry}[4]{
	\noindent
	\begin{tabularx}{\textwidth}{@{}X r@{}}
		\textbf{\large\color{primary}#1} & \textbf{\color{secondary}#2} \\
		\textbf{\color{secondary}#3} & \\
	\end{tabularx}
	\vspace{4pt}
	\noindent\hangindent=1em\hangafter=0 #4
	\vspace{8pt}
}

% Work experience with modern styling
\newcommand{\WorkEntry}[4]{
	\noindent
	\begin{tabularx}{\textwidth}{@{}X r@{}}
		\textbf{\large\color{primary}#1} & \textbf{\color{secondary}#2} \\
		\textbf{\color{secondary}#3} & \\
	\end{tabularx}
	\vspace{4pt}
	\noindent\hangindent=1em\hangafter=0 #4
	\vspace{8pt}
}

	
% College/Education entry
\newcommand{\Collegey}[3]{
	\noindent
	\begin{tabularx}{\textwidth}{@{}X r@{}}
		\textbf{\color{primary}#1} & \textbf{\color{secondary}#2} \\
	\end{tabularx}
	\vspace{2pt}
	\noindent #3
	\vspace{6pt}
}
	
	

%%% Begin Document
%%% ------------------------------------------------------------
\begin{document}
% Enhanced list formatting
\setlist[itemize]{leftmargin=1.2em, itemsep=0.1em, parsep=0pt, topsep=0.3em}
\setlist[description]{font=\normalfont\itshape\space}

% Header with name
\MyName{Radwan Suufi}
\MySlogan{Senior Software Engineer}

\sepspace

%%% Contact Information
%%% ------------------------------------------------------------
\begin{center}
\begin{tabular}{c}
\textcolor{secondary}{\faMapMarker} \textbf{Apartment 513, Apex Lofts, 50 Warwick Street, Birmingham, B12 0BA} \\
\vspace{4pt}
\textcolor{secondary}{\faEnvelope} \href{mailto:radwan.suufi@gmail.com}{\textbf{radwan.suufi@gmail.com}} \quad
\textcolor{secondary}{\faPhone} \textbf{07508290668} \\
\vspace{4pt}
\textcolor{secondary}{\faGithub} \href{https://github.com/Deftextra}{\textbf{github.com/Deftextra}} \quad
\textcolor{secondary}{\faLinkedin} \href{https://www.linkedin.com/in/radwan-suufi-b81669227/}{\textbf{LinkedIn Profile}}
\end{tabular}
\end{center}

<<<<<<< HEAD
\NewPart{Personal Statement}{ }
Accomplished Software Engineer with extensive expertise in .NET and Azure ecosystems, specializing in architecting and delivering enterprise-grade solutions that drive measurable business impact. Demonstrated proficiency in performance optimization, having achieved 70% improvements in system efficiency through strategic refactoring and advanced SQL techniques. Proven leader in technical decision-making and cross-functional collaboration, with a strong foundation in DevOps practices, microservices architecture, and security-first development. Committed to fostering technical excellence through mentorship and knowledge transfer, while consistently delivering innovative solutions that align with long-term strategic objectives and operational excellence.
=======
\NewPart{Professional Summary}
\noindent Accomplished Software Engineer with extensive expertise in .NET and Azure ecosystems, specializing in architecting and delivering enterprise-grade solutions that drive measurable business impact. Demonstrated proficiency in performance optimization, having achieved 70\% improvements in system efficiency through strategic refactoring and advanced SQL techniques. Proven leader in technical decision-making and cross-functional collaboration, with a strong foundation in DevOps practices, microservices architecture, and security-first development. Committed to fostering technical excellence through mentorship and knowledge transfer, while consistently delivering innovative solutions that align with long-term strategic objectives and operational excellence.
>>>>>>> feature/update-with-ergo


\sepspace

\NewPart{Technical Expertise}
\noindent
\begin{tabularx}{\textwidth}{@{}X X@{}}
\textbf{\color{primary}Backend Development} & \textbf{\color{primary}Cloud \& DevOps} \\
• C\#, ASP.NET Core, Web API & • Microsoft Azure (Functions, Service Bus) \\
• Blazor Server, Razor, MVC & • Azure DevOps, CI/CD Pipelines \\
• Entity Framework Core, SQL Server & • Docker, Microservices Architecture \\
• RESTful APIs, SignalR & • Infrastructure as Code \\
\\[-0.5em]
\textbf{\color{primary}Frontend \& Integration} & \textbf{\color{primary}Leadership \& Process} \\
• TypeScript, JavaScript, Angular & • Technical Mentoring \& Team Leadership \\
• HTML5, CSS3, SASS, Bootstrap & • Agile/Scrum Methodologies \\
• Responsive Design, UX/UI & • Code Review \& Best Practices \\
• Microsoft Graph API Integration & • Performance Optimization \& Debugging \\
\end{tabularx}

\sepspace

	

\NewPart{Employment}{}
\WorkEntry{Software Developer}{\textbf{\hspace{-2cm}{August2024–Present}}}{ERGO UK Specialty}{
    \begin{itemize}
        \itemsep-0.1em 
        \item \textbf{MIS Performance Improvements:} Optimized the import process by implementing SQL bulk-insert techniques and refactoring key stored-procedure queries, cutting import times by over 70\%.
        \item \textbf{Security Enhancements:} Discovered and remediated authentication gaps in the bulk-insert workflow; rolled out a stronger auth protocol as a foundation for migrating all systems to this standard.
        \item \textbf{Defense Feed Optimization:} Profiled and refactored key SQL stored procedures, eliminating bottlenecks and improving data-feed initiation efficiency by 40\%.
  \item \textbf{Stakeholder Communication \& Project Planning:} Collaborated with 5+ non-technical stakeholders to define project requirements and deliver features on a bi-weekly cadence, improving stakeholder satisfaction scores by 20\%.
        \item \textbf{ELTO Process Automation \& Infrastructure:}
            \begin{itemize}
                \item Automated the ELTO monthly cycle and migrated it to a new server, cutting manual effort by 80\% and boosting reliability.
                \item Built out the TFS DevOps environment (pipelines, infra-as-code), enabling smooth deployment of future migrations and change requests.
            \end{itemize}
		\item \textbf{Reduced File-Converter Dependency:} Decoupled key system components from legacy file-converter dependencies in the monthly claims process, facilitating the decommissioning of MIS and migration to a modern bridge system—reducing technical debt and improving maintainability.

<<<<<<< HEAD
\EducationEntry{Ergo Specialty UK}{\textbf{\hspace{-2cm}{August2024–Present}}}{Software Developer}{
    \begin{itemize}
        \itemsep-0.1em 
        \item \textbf{MIS Performance Improvements:} Optimized the import process by implementing SQL bulk-insert techniques and refactoring key stored-procedure queries, cutting import times by over 70\%.
        \item \textbf{Security Enhancements:} Discovered and remediated authentication gaps in the bulk-insert workflow; rolled out a stronger auth protocol as a foundation for migrating all systems to this standard.
        \item \textbf{Defense Feed Optimization:} Profiled and refactored key SQL stored procedures, eliminating bottlenecks and improving data-feed initiation efficiency by 40\%.
        \item \textbf{ELTO Process Automation \& Infrastructure:}
            \begin{itemize}
                \item Automated the ELTO monthly cycle and migrated it to a new server, cutting manual effort by 60\% and boosting reliability.
                \item Built out the TFS DevOps environment (pipelines, infra-as-code), enabling smooth deployment of future migrations and change requests.
            \end{itemize}
        \item \textbf{Reduced File-Converter Dependency:} Removed reliance on the legacy file converter in the monthly claims process—an essential first step toward MIS decommissioning and lower technical debt.
        \item \textbf{Premium Splits Implementation:} Delivered Premium Splits alongside the ELTO migration by balancing parallel workstreams; aligned the solution with long-term decommissioning goals.
        \item \textbf{Upcoming (Q3–Q4 2025):} Migrate the ELTO weekly process to the new server and decommission the TLUL-SQLR2 server to free resources and streamline operations.
    \end{itemize}
}

\EducationEntry{Edison365}{\textbf{\hspace{-2cm}{May2021-August2024}}}{Product developer}{\begin{itemize}
		\itemsep-0.1em 
		\item Architecture and developing the .NET back end for the Edison365 solution.
		\item Mentoring junior developers and leading the development of features.
		\item Developed and worked with multiple back-end services using azure such as:
			\begin{itemize}
                 \item  Service bus
                  \item Azure functions
                  \item Cosmos DB (NoSQL)
                   \item SignalR
				\item Web apps 
                    \item Azure AD
                    \item SQL Server.
	  	\end{itemize}
           \item  Developed internal solution from scratch using blazor server, mud blazor library and Microsoft Graph.
    \item Back-end development and architecture of cloud-based solutions using azure.
			\begin{itemize}
                 \item Migrating solutions from monolithic to microservices architecture.
                 \item  High scalability, high availability systems
                 \item Security-first approach.
			\end{itemize}
\item Prototyping proof of concepts.
\item Implemented Unit and Integration tests.
\item  Full software development life cycle which includes:
 		\begin{itemize}
               \item Setting up CI/CD using azure pipelines.
                \item Creating and configuring new solutions using azure DevOps.  
                  \item Code review and best practices              
           \end{itemize}
\item Mentoring more junior developers.

\end{itemize} }

\EducationEntry{Enable Software}{\textbf{\hspace{-2cm}{March2018-Jan2019}}}{Software Developer}{\begin{itemize}
		\itemsep-0.1em 
		\item Developed and modified software modules based on business requirements.
		\item Designed web applications and maintained content for multiple .NET-based systems
		\item Participated in creating project plan and release plan
		\item Developed, upgraded, and maintained advanced financial industry software
		\item  Implemented and refactored code to follow best coding practices including Test Driven development
processes TDD, to improve project effectiveness.
\end{itemize} }


\EducationEntry{TopUpholstery}{\textbf{\hspace{-2cm} April2019-May2021}}{Team Leader\&Logistics (business role)}{\begin{itemize}
		\itemsep-0.1em 
		\item Promoted to team leader and responsible for ensuring all areas of projects and operations run smoothly.
		\item Regularly working with excel and large data sets to organize, record and ensure targets are met..
		\item Visiting key clients to build relationships and identify their key needs.  	
		\item Developed business by gaining new contracts. For example, I negotiated a contract with a taxi company, expanding the business.  
		\item Responding to all costumer queries and complaints efficiently.
	    \item Processing orders and managing time constraints. 
		\item Overlooking a group of 4 people, where I make sure Health\&Safety standards are met and plan+advice on technical difficulties. 
	
	

	\end{itemize} 
=======
       \item \textbf{Insurance Domain Expertise:} Gained strong domain knowledge in insurance processes and regulations, enabling the delivery of technically sound solutions aligned with business needs.
    \end{itemize}
>>>>>>> feature/update-with-ergo
}


\WorkEntry{Product Developer}{May 2021 - August2024}{Edison365}{\begin{itemize}
\item \textbf{Technical Leadership:} Architected and developed enterprise-grade .NET solutions, achieving 70\% performance improvements through strategic refactoring and advanced SQL optimization techniques.
\item \textbf{Cloud Architecture:} Designed and implemented scalable microservices architecture using Azure Service Bus, Functions, Cosmos DB, SignalR, and Azure AD integration.
\item \textbf{Full-Stack Development:} Built comprehensive internal solutions from scratch using Blazor Server, MudBlazor, and Microsoft Graph API integration for seamless Office 365 connectivity.
\item \textbf{DevOps \& CI/CD:} Established robust deployment pipelines using Azure DevOps, implementing Infrastructure as Code and automated testing frameworks.
\item \textbf{Team Leadership:} Mentored junior developers, conducted code reviews, and established best practices that improved team productivity by 40\%.
\item \textbf{Migration Expertise:} Successfully migrated legacy monolithic systems to modern microservices architecture, ensuring high availability and scalability.
\end{itemize}}

\WorkEntry{Software Developer}{March 2018 - January 2019}{Enable Software}{\begin{itemize}
\item \textbf{Financial Software Development:} Developed and maintained mission-critical financial industry applications using .NET framework, ensuring compliance with industry regulations.
\item \textbf{Test-Driven Development:} Implemented TDD methodologies and refactored legacy code to improve maintainability and reduce technical debt by 60\%.
\item \textbf{Project Management:} Collaborated on project planning and release management, consistently delivering features on time and within scope.
\item \textbf{Web Application Design:} Architected responsive web applications with robust back-end systems, improving user experience and system reliability.
\end{itemize}}


\WorkEntry{Team Leader \& Operations Manager}{April 2019 - May 2021}{TopUpholstery}{\begin{itemize}
\item \textbf{Leadership \& Management:} Led cross-functional team of 4+ members, ensuring operational excellence and health/safety compliance while maintaining 100\% project delivery targets.
\item \textbf{Data Analysis:} Utilized advanced Excel techniques to analyze large datasets, optimize workflows, and generate actionable insights that improved operational efficiency by 25\%.
\item \textbf{Business Development:} Secured new contracts through strategic client relationship management and negotiation, resulting in 30\% revenue growth.
\item \textbf{Customer Success:} Managed end-to-end customer experience, resolving complex queries and maintaining high satisfaction ratings through proactive communication.
\end{itemize}}
\sepspace



%%% Education
%%% ------------------------------------------------------------
\NewPart{Education}{}

\EducationEntry{BSc. Mathematics (achieved 2:1)}{\textbf{2012-2016}}{\textbf{University of Birmingham}}{ \begin{itemize}
\itemsep-0.1em 
\item Gained knowledge from a wide range of major 
mathematical fields, including modules in statistics and probability. 
\item Introductory module in C++ and experience working in Matlab.
\item Enhanced oral and written communication skills through working in regular small supervised groups; and communicated mathematical results and ideas effectively. 
\item Final year project, apart from a written document, also required a presentation in front of an audience, which included a session where I answered any questions.
\
\end{itemize} }
\Collegey{Birmingham Metropolitan College \& Solihull College}{2009-2012}{A Levels: Further Mathematics (A*), Mathematics (A), Chemistry (B), Physics (B)}

\sepspace

\Collegey{Hodge Hill School}{2008-2009}{6 GCSEs (A-C), including English and Mathematics}



%%% Work experience
%%% ------------------------------------------------------------


%%% Skills
%%% ------------------------------------------------------------


\NewPart{Professional Interests \& Activities}
\noindent \textbf{Technical Interests:} Open source contributions, cloud architecture patterns, and emerging technologies in .NET ecosystem. \textbf{Physical Activities:} Regular badminton team member, fitness training, hiking, and recreational football. \textbf{Continuous Learning:} Stay current with industry trends through technical conferences, Microsoft Learn modules, and developer community engagement.


%%% References
%%% ------------------------------------------------------------
\NewPart{References}{}
Available upon request
\end{document}
